---
title: "flat_extract_map.Rmd"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r development, include=FALSE}
library(testthat)
library(assertthat)
```

## Extract map with desired densities

This function allows, from a density map `density_obj` (density object of the `dsims` packages), to provide a map of class `sf` (data.frame).      
It allows to recalculate the correct density ratios of the provided map according to the desired number of individuals in the area `N`.  

```{r function-extract_map}

#' Extract map with the desired density
#'
#' This function allows, from a density map `density_obj` (density object of the `dsims` packages), to provide a map of class `sf` (data.frame).It allows to recalculate the correct density ratios of the provided map according to the desired number of individuals in the area `N`. 
#' @param density_obj Density object from dsims package. The map containing information density ratio on the study area.
#' @param N Numeric. The number of individuals desired in the area.
#' @param crs Numeric. Projection system.
#'
#' @importFrom sf st_sf st_area
#' @importFrom dplyr mutate pull
#' @importFrom units drop_units
#' @importFrom assertthat assert_that
#'
#' @return sf object. The map with the densities corresponding to the number of individuals desired in the study area. 
#' @export


extract_map <- function(density_obj, N, crs) {
  
  
  # Function checks
  
  
  assert_that(inherits(density_obj, "Density"))
  
  # Function
  
  map_obj <- density_obj@density.surface %>%
    as.data.frame() %>%
    st_sf(crs = crs) %>%
    mutate(area = st_area(.)) %>%
    mutate(area_grid = density_obj@x.space * density_obj@y.space) %>%
    drop_units() %>%
    filter(area == area_grid)
  
  area <- sum(map_obj$area)
  
  average_density_m <- N / area
  
  map_obj <- map_obj %>%
    mutate(density_m = average_density_m * density / mean(density, na.rm = TRUE)) %>%
    mutate(density_km = (average_density_m * density / mean(density, na.rm = TRUE)) * 1000000) %>%
    
    
    return(map_obj)
  
}

```

### Example

An example of this function use a dataset of density `dataset_density` created thanks to the package `dsims`. 

From this density object, the aim is to create a map with the correct densities. Here a density corresponding to 500 individuals in the study area.     

```{r examples-extract_map, warning = FALSE}

data(dataset_density)

map <- extract_map(density_obj = dataset_density,
                   N = 500,
                   crs = 2154)


head(map)

```

```{r tests-extract_map}

library(testthat)
library(dplyr)


test_that("extract_map works", {
  expect_true(inherits(extract_map, "function")) 
})


test_that("test conformite simulate_ind", {
  
  data("dataset_density")
  
  test <- dataset_density %>%
    extract_map(N = 500,
                crs = 2154) %>%
    slice(1:5)

exp <- structure(list(strata = c("St Andrews bay", "St Andrews bay", 
"St Andrews bay", "St Andrews bay", "St Andrews bay"), density = c(10.5870697722385, 
10.0915244093542, 9.45666871410529, 8.74640906414673, 8.02399470530445
), x = c(-159390.409885506, -157390.409885506, -155390.409885506, 
-153390.409885506, -151390.409885506), y = c(6244043.1524534, 
6244043.1524534, 6244043.1524534, 6244043.1524534, 6244043.1524534
), area = c(4e+06, 4e+06, 4e+06, 4e+06, 4e+06), area_grid = c(4e+06, 
4e+06, 4e+06, 4e+06, 4e+06), density_m = c(1.1143756163953e-06, 
1.06221541710539e-06, 9.95391666819911e-07, 9.20631034062134e-07, 
8.44591018859943e-07), density_km = c(1.1143756163953, 1.06221541710539, 
0.995391666819911, 0.920631034062134, 0.844591018859943), geometry = structure(list(
    structure(list(structure(c(-160390.409885506, -160390.409885506, 
    -158390.409885506, -158390.409885506, -160390.409885506, 
    6243043.1524534, 6245043.1524534, 6245043.1524534, 6243043.1524534, 
    6243043.1524534), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", 
    "sfg")), structure(list(structure(c(-158390.409885506, -158390.409885506, 
    -156390.409885506, -156390.409885506, -158390.409885506, 
    6243043.1524534, 6245043.1524534, 6245043.1524534, 6243043.1524534, 
    6243043.1524534), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", 
    "sfg")), structure(list(structure(c(-156390.409885506, -156390.409885506, 
    -154390.409885506, -154390.409885506, -156390.409885506, 
    6243043.1524534, 6245043.1524534, 6245043.1524534, 6243043.1524534, 
    6243043.1524534), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", 
    "sfg")), structure(list(structure(c(-154390.409885506, -154390.409885506, 
    -152390.409885506, -152390.409885506, -154390.409885506, 
    6243043.1524534, 6245043.1524534, 6245043.1524534, 6243043.1524534, 
    6243043.1524534), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", 
    "sfg")), structure(list(structure(c(-152390.409885506, -152390.409885506, 
    -150390.409885506, -150390.409885506, -152390.409885506, 
    6243043.1524534, 6245043.1524534, 6245043.1524534, 6243043.1524534, 
    6243043.1524534), .Dim = c(5L, 2L))), class = c("XY", "POLYGON", 
    "sfg"))), class = c("sfc_POLYGON", "sfc"), precision = 0, bbox = structure(c(xmin = -160390.409885506, 
ymin = 6243043.1524534, xmax = -150390.409885506, ymax = 6245043.1524534
), class = "bbox"), crs = structure(list(input = "EPSG:2154", 
    wkt = "PROJCRS[\"RGF93 / Lambert-93\",\n    BASEGEOGCRS[\"RGF93\",\n        DATUM[\"Reseau Geodesique Francais 1993\",\n            ELLIPSOID[\"GRS 1980\",6378137,298.257222101,\n                LENGTHUNIT[\"metre\",1]]],\n        PRIMEM[\"Greenwich\",0,\n            ANGLEUNIT[\"degree\",0.0174532925199433]],\n        ID[\"EPSG\",4171]],\n    CONVERSION[\"Lambert-93\",\n        METHOD[\"Lambert Conic Conformal (2SP)\",\n            ID[\"EPSG\",9802]],\n        PARAMETER[\"Latitude of false origin\",46.5,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8821]],\n        PARAMETER[\"Longitude of false origin\",3,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8822]],\n        PARAMETER[\"Latitude of 1st standard parallel\",49,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8823]],\n        PARAMETER[\"Latitude of 2nd standard parallel\",44,\n            ANGLEUNIT[\"degree\",0.0174532925199433],\n            ID[\"EPSG\",8824]],\n        PARAMETER[\"Easting at false origin\",700000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8826]],\n        PARAMETER[\"Northing at false origin\",6600000,\n            LENGTHUNIT[\"metre\",1],\n            ID[\"EPSG\",8827]]],\n    CS[Cartesian,2],\n        AXIS[\"easting (X)\",east,\n            ORDER[1],\n            LENGTHUNIT[\"metre\",1]],\n        AXIS[\"northing (Y)\",north,\n            ORDER[2],\n            LENGTHUNIT[\"metre\",1]],\n    USAGE[\n        SCOPE[\"unknown\"],\n        AREA[\"France\"],\n        BBOX[41.15,-9.86,51.56,10.38]],\n    ID[\"EPSG\",2154]]"), class = "crs"), n_empty = 0L)), row.names = c(NA, 
-5L), class = c("sf", "data.frame"), sf_column = "geometry", agr = structure(c(strata = NA_integer_, 
density = NA_integer_, x = NA_integer_, y = NA_integer_, area = NA_integer_, 
area_grid = NA_integer_, density_m = NA_integer_, density_km = NA_integer_
), class = "factor", .Label = c("constant", "aggregate", "identity"
)))

expect_equal(object = test,
             expected = exp)

expect_is(test, "data.frame")

})

test_that("test erreur extract_map", {
  
  data(iris)
  
  expect_error(object = extract_map(density_obj =  iris,
                                    N = 500,
                                    crs = 2154))
  
})

```

## Plot map

This fonction allows to plot the map created with the `extract_map` function. It is nessary to use the `map_obj`, a sf dataframe, contaning at least, a column `density_km`. The `title` and the `legend` can be personnalized.


```{r function-plot_map}

#' Plot map
#'
#' This fonction allows to plot the map created with the extract_map function. It is nessary to use the map_obj, a sf dataframe, contaning at least, a column density_km. The title and the legend can be personnalized.
#' @param map_obj Dataframe. Sf map to plot.
#' @param title Character. Title.
#' @param legend Character. Legend for the color gradient.
#'
#' @importFrom ggplot2 ggplot geom_sf aes coord_sf scale_fill_gradientn geom_point scale_size labs theme element_text element_blank theme_set theme_bw unit
#' @importFrom ggspatial annotation_scale annotation_north_arrow north_arrow_fancy_orienteering
#' @importFrom viridisLite viridis
#' @importFrom sp bbox
#' @importFrom sf as_Spatial
#' @importFrom assertthat assert_that
#'
#' @return ggplot object. The study area with the gradient of density (ind/km2).
#' @export 


plot_map <- function(map_obj, legend = "Density (ind/km2)", title = ""){
  
  # Function checks
  
  
  assert_that(inherits(map_obj, "sf"))
  if (!all(c("density_km") %in% names(map_obj))) {stop("map_obj must contain `density_km` column. Verify your column names.")}
  assert_that(is.numeric(map_obj$density_km))
  
  
  # Function 
  
  theme_set(theme_bw())
  
  xlim <- bbox(as_Spatial(map_obj))[1, ]
  ylim <- bbox(as_Spatial(map_obj))[2, ]
  
  ggplot() +
    geom_sf(data = map_obj, aes(fill = density_km), color = NA) +
    scale_size(name = "Nb ind", breaks = 0:3) +
    coord_sf(xlim = xlim, ylim = ylim) +
    annotation_scale(location = "br", width_hint = 0.5) +
    annotation_north_arrow(location = "tr",
                           which_north = "true",
                           height = unit(0.8, "cm"),
                           width = unit(0.8, "cm"),
                           pad_x = unit(0.2, "cm"),
                           pad_y = unit(0.1, "cm"),
                           style = north_arrow_fancy_orienteering) +
    scale_fill_gradientn(name = legend,
                         colors = viridis(256)) +
    theme(legend.position = "right",
          legend.key.width = unit(0.5, "cm"),
          plot.title = element_text(lineheight = 0.8, face = "bold"),
          axis.text = element_text(size = 6),
          axis.title.x = element_blank(),
          axis.title.y = element_blank())
}
```

### Example

An example of this function use a dataset of density `dataset_density` created thanks to the package `dsims`. 

From this density object, a map is created thanks to the `extract_map` function. Then the function `plot_map` allows to plot the map with the correct densities.


```{r examples-plot_map, warning = FALSE}

data(dataset_density)

map <- extract_map(density_obj = dataset_density,
                   N = 500,
                   crs = 2154)

plot_map(map_obj = map)

```

```{r tests-plot_map}
library(testthat)
library(dplyr)


test_that("plot_map works", {
  
  data("dataset_map")
  
  expect_true(inherits(plot_map(map_obj = dataset_map), "ggplot"))
  expect_true(inherits(plot_map, "function")) 
  
})


test_that("test erreur plot_obs", {
  
  data(iris)
  data("dataset_map")
  
  expect_error(object = plot_map(map_obj = iris))
  
  
  dataset_map_test <- dataset_map %>%
    rename(nop = density_km)
  
  expect_error(object = plot_map(map_obj = dataset_map_test))
  
  dataset_map_test <- dataset_map
  dataset_map_test$density_km[5] <- "nop"
  
  expect_error(object = plot_map(map_obj = dataset_map_test))
  
})
```



```{r development-inflate, eval=FALSE}
# Run but keep eval=FALSE to avoid infinite loop
# Execute in the console directly
fusen::inflate(flat_file = "dev/flat_extract_map.Rmd", 
               vignette_name = "Extract map",
               open_vignette = FALSE,
               check = FALSE,
               overwrite = TRUE)
```
